### 2013-01-15 edupar-13/landslide.tex
remove unnecessary citations

Landslide is an experimental tool for helping kernel authors find and debug concurrency errors.
It is based on the technique of systematic exploration~\cite{verisoft}, a way of exploring the state space of different possible thread interleavings in a concurrent system.
It follows in the footsteps of related tools such as CHESS~\cite{chess}, dBug~\cite{dbug-ssv}, and DeMeter~\cite{demeter}, but is the first tool we know of to apply systematic exploration in a kernel development environment.

@@

Of course, additional decision points are necessary to expose more subtle race conditions. We provide an interface for adding new decision points to expand the state space, described in Section~\ref{sec:decision}.
In order to cope with the exponentially-growing nature of state spaces with many decision points,
Landslide uses the Dynamic Partial Order Reduction algorithm~\cite{dpor} to identify and prune redundant thread interleavings, the specifics of which are beyond the scope of this educational work~\cite{landslide}.
We also provide an interface for helping Landslide further reduce the state space by considering decision points only from certain components of the kernel, which we discuss in Section~\ref{sec:focusing}.

>>>>

Landslide is an experimental tool for helping kernel authors find and debug concurrency errors.
It is based on the technique of systematic exploration~\cite{verisoft}, a way of exploring the state space of different possible thread interleavings in a concurrent system.
It follows in the footsteps of related tools such as
CHESS~\cite{chess} and dBug~\cite{dbug-ssv}, but is the first tool we know of to apply systematic exploration in a kernel development environment.

@@

Of course, additional decision points are necessary to expose more subtle race conditions. We provide an interface for adding new decision points to expand the state space, described in Section~\ref{sec:decision}.
In order to cope with the exponentially-growing nature of state spaces with many decision points,
\shortversion{
we also provide an interface for making Landslide consider
}{
Landslide uses the Dynamic Partial Order Reduction algorithm~\cite{dpor} to identify and prune redundant thread interleavings, the specifics of which are beyond the scope of this educational work~\cite{landslide}.
We also provide an interface for helping Landslide further reduce the state space by considering
}
decision points only from certain components of the kernel, which we discuss in Section~\ref{sec:focusing}.
